\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?

### 2017-12-13 Data_csv/paper.tex
ready to read folks !

\usepackage[
%backend=biber, 
natbib=true, 
style=numeric, 
sorting=none
]{biblatex}
\addbibresource{\jobname.bib}
\vspace{-2cm}
\title{\LARGE \bf
Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution ?
}

@@

Toluene is a solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry. Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic\cite{toluene}. 
When such event happens, one way to treat those is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.

The microorganisms we chose for our experiment were \textit{Pseudomonas putida} (PP) and \textit{Pseudomonas veronii} (PV), both able to metabolize toluene \cite{pseudomonas_putida} \cite{Pseudomonas_Veronii}. The bacterial community on which we tested this procedure was extracted from sand (sand community (SC)collected at St-Sulpice beach, Switzerland).

@@

\subsection{Inoculation}
We put 20 mL of mixed carbon media [0.1mM] in nine flasks, and 20 mL of MM 1x in the other nine, where we added 200 µL toluene  50\% (100 µL toluene and 100 µL 2,2,4,4,6,8,8-Heptamethylnonane (HMN)\footnote{Oil used with volatile solvent to decrease their toxicity by slowing it's release in the medium. Ref. https://www.sigmaaldrich.com/catalog/product/aldrich/128511?lang\linebreak[0]=fr\&region=CH, Dec. 2017}) in a tip sealed at the bottom. Toluene being volatile, it will then evaporate and dissolve in the liquid media. It will then be the only source of carbon. We quantified the cells by using flow cytometry, and calculated to put $10^{6}$ cells/mL in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PPSC and PVSC flasks. The flasks containing toluene were sealed to avoid toluene leaks (Fig. \ref{flasks}).
They were incubated at 25°C and constantly shaken at 110rpm during 48 hours.

@@

\begin{figure}[H]
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering

@@

	\end{subfigure}
	\caption{Fig. \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Fig. \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
	\label{scatterplot}
\end{figure}	
\vspace{-0.2cm}
On Fig. \ref{scatter1} is a scatter plot of an unstained sample of PPSC. On the vertical axis is represented red fluorescence. The horizontal axis shows green fluorescence. A big black cluster and a red one above it can be observed. The black cluster is composed of SC cells and remaining particles. They show  low red and green fluorescence values. The PP cells express mCherry and therefore show red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.

@@

%\begin{figure}[H]
%	\centering
%	
%	\includegraphics[width=9.3cm]{totcount_mixC1.PNG}
%	\caption{ADD CAPTION}
%	\label{totcountmixC1text}
%\end{figure}
%\begin{figure}[H]
%	\centering
%	
%	\includegraphics[width=9.3cm]{totcount_tol1.PNG}
%	\caption{ADD CAPTION}
%	\label{totcounttol1text}
%\end{figure}
\begin{figure}[H]

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{totcount_mixC1.PNG}
		\caption{}
		\label{totcountmixC1text}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{totcount_tol1.PNG}
		\caption{}
		\label{totcounttol1text}
	\end{subfigure}
	\caption{Fig. \ref{totcountmixC1text}: Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week. Fig. \ref{totcounttol1text} : Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
	\label{totcount1}

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first week is represented in Fig. \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue curve).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow curves).
We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a better growth but has no effect in the mix carbon media. In addition, the effect of the media on SC is important in absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{totcount_mixC2.PNG}
		\caption{}
		\label{totcountmixC2text}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{totcount_tol2.PNG}
		\caption{}		
		\label{totcounttol2text}
	\end{subfigure}
	\caption{Fig. \ref{totcountmixC2text}: Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week. Fig. \ref{totcounttol2text} : Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
	\label{totcount2}

@@

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second week is represented in Fig. \ref{SCgrowth2}.
In contrast with the first week, SC was able to grow in toluene. It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that the sand community we extracted behaved differently from one week to another and thus cannot be considered similar. Therefore, we won't be able to compare the results from the two weeks. 
The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow higher alone than in presence of PV.\newline

@@

@@

We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref {problemsyto}.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{}
		\label{problemw1}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{problemw2.PNG}
		\caption{}
		\label{problemw2}
	\end{subfigure}

\caption{Fig. \ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences. Fig. \ref{problemw2} : Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
\label{problemsyto}

@@

\begin{figure}[H]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{aucw1.PNG}
		\caption{}
		\label{aucw1}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=9cm]{aucw2.PNG}
		\caption{}
		\label{aucw2}
	\end{subfigure}
\caption{Week 1
	From left to right: MixC\_SC\_w1:  Sand community in mixed carbon; MixC\_PP: Pseudomonas Putida in mixed carbon; MixC\_PPSC\_SC: Sand community + Pseudomonas Putida in mixed carbon, “SYTO-9” gate; MixC\_PPSC\_PP: Sand community + Pseudomonas Putida in mixed carbon, “mChe + SYTO\_9” gate; MixC\_PPSC\_SC: Sand community + Pseudomonas Putida in mixed carbon, sum of “SYTO-9 “ gate and “mChe + SYTO\_9” gate ;
	Tol\_SC\_w1:  Sand community in Toluene; Tol\_PP: Pseudomonas Putida in toluene; Tol\_PPSC\_SC: Sand community + Pseudomonas Putida in toluene, “SYTO-9” gate; Tol\_PPSC\_PP: Sand community + Pseudomonas Putida in toluene, “mChe + SYTO\_9” gate; Tol\_PPSC\_SC: Sand community + Pseudomonas Putida in toluene, sum of “SYTO-9 “ gate and “mChe + SYTO\_9” gate 
}
\end{figure}

>>>>

\usepackage[
%backend=biber, 
natbib=true, 
style=numeric, 
sorting=none
]{biblatex}
\addbibresource{\jobname.bib}
\vspace{-2cm}
\title{\LARGE \bf
Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?
}

@@

Toluene is an organic solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry. Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic\cite{toluene}. 
When such event happens, one way to treat those is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.

The microorganisms we chose for our experiment were \textit{Pseudomonas putida} (PP) and \textit{Pseudomonas veronii} (PV), both able to metabolize toluene \cite{pseudomonas_putida} \cite{Pseudomonas_Veronii}. The bacterial community on which we tested this procedure was extracted from sand (sand community (SC) collected at St-Sulpice beach, Switzerland).

@@

\subsection{Inoculation}
We put 20 mL of mixed carbon media [0.1mM] in nine flasks, and 20 mL of MM 1x in the other nine, where we added 200 µL toluene  50\% (100 µL toluene and 100 µL 2,2,4,4,6,8,8-Heptamethylnonane (HMN)\footnote{Oil used with volatile solvent to decrease their toxicity by slowing its release in the medium. Ref. https://www.sigmaaldrich.com/catalog/product/aldrich/128511?lang\linebreak[0]=fr\&region=CH, Dec. 2017}) in a tip sealed at the bottom. Toluene being volatile, it will then evaporate and dissolve in the liquid media. It will then be the only source of carbon. We quantified the cells by using flow cytometry, and calculated to put $10^{6}$ cells/mL in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PPSC and PVSC flasks. The flasks containing toluene were sealed to avoid toluene leaks (Fig. \ref{flasks}).
They were incubated at 25°C and constantly shaken at 110rpm during 48 hours.

@@

\begin{figure}
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering

@@

	\end{subfigure}
	\caption{Fig. \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Fig. \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
	\label{scatterplot}
\end{figure}

On Fig. \ref{scatter1} is a scatter plot of an unstained sample of PPSC. On the vertical axis is represented red fluorescence. The horizontal axis shows green fluorescence. A big black cluster and a red one above it can be observed. The black cluster is composed of SC cells and remaining particles. They show  low red and green fluorescence values. The PP cells express mCherry and therefore show red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.

@@

%\begin{figure}[H]
%	\centering
%	
%	\includegraphics[width=9.3cm]{totcount_mixC1.PNG}
%	\caption{ADD CAPTION}
%	\label{totcountmixC1text}
%\end{figure}
%\begin{figure}[H]
%	\centering
%	
%	\includegraphics[width=9.3cm]{totcount_tol1.PNG}
%	\caption{ADD CAPTION}
%	\label{totcounttol1text}
%\end{figure}
%\begin{figure}[H]
%	
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=9cm]{totcount_mixC1.PNG}
%		\caption{}
%		\label{totcountmixC1text}
%	\end{subfigure}
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=9cm]{totcount_tol1.PNG}
%		\caption{}
%		\label{totcounttol1text}
%	\end{subfigure}
%	\caption{Fig. \ref{totcountmixC1text}: Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week. Fig. \ref{totcounttol1text} : Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
%	\label{totcount1}
%\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=9cm]{totcount_mixC1.PNG}
	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week.}
	\label{totcountmixC1text}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=9cm]{totcount_tol1.PNG}
	\caption{Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
	\label{totcounttol1text}
\end{figure}

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first week is represented in Fig. \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue curve).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow curves).
We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a better growth but has no effect in the mix carbon media. In addition, the effect of the media on SC is important in absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc1.png}
	\caption{AUC Week 1 SC}
	\label{aucscw1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpp1.png}
	\caption{AUC Week 1 PP}
	\label{aucppw1}
\end{figure}

@@

%\begin{figure}[H]
%	
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=9cm]{totcount_mixC2.PNG}
%		\caption{}
%		\label{totcountmixC2text}
%	\end{subfigure}
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=9cm]{totcount_tol2.PNG}
%		\caption{}		
%		\label{totcounttol2text}
%	\end{subfigure}
%	\caption{Fig. \ref{totcountmixC2text}: Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week. Fig. \ref{totcounttol2text} : Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
%	\label{totcount2}
%	
%\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_mixC2.PNG}
	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.}
	\label{totcountmixC2text}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_tol2.PNG}
	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
	\label{totcounttol2text}
\end{figure}
\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second week is represented in Fig. \ref{SCgrowth2}.
In contrast with the first week, SC was able to grow in toluene. It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that the sand community we extracted behaved differently from one week to another and thus cannot be considered similar. Therefore, we won't be able to compare the results from the two weeks. 
The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow higher alone than in presence of PV.\newline

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc2.png}
	\caption{AUC Week 2 SC}
	\label{aucscw2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpv2.png}
	\caption{AUC Week 2 PV}
	\label{aucppw2}
\end{figure}

@@

We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref{problemw1} and \ref{problemw2}.

@@

		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences.}
		\label{problemw1}
\end{figure}

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw2.PNG}
		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
		\label{problemw2}

%\caption{Fig. \ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences. Fig. \ref{problemw2} : Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
%\label{problemsyto}

@@
